---
title: "Data_Challenge_4_AAnderson"
subtitle: "GitHub Link: https://github.com/ashleymaree/Data_Challenge_4.git"
author: "Ashley Anderson"
date: "11/11/2020"
output: html_document
---
```{r,echo=FALSE}
knitr::opts_chunk$set(cache=TRUE, error=FALSE, message=FALSE, warning=FALSE, tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r}
## read in the data
park_visits <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-17/national_parks.csv")
state_pop <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-17/state_pop.csv")
## load libraries
library(tidyverse) 
```

**Question 1a: Make a figure that shows the trend in the raw number of park visitors over time for 3 parks: Crater Lake, Joshua Tree, and Zion.**

```{r}
CJTZ_data <- park_visits %>% ## create dataframe for graph #1
  subset(year!='Total') %>% ## remove "Total" column from dataframe
  select(year, parkname, visitors, state) %>% ## select only columns of interest for both graphs
  mutate(visitors_mil = visitors/1000000) %>% ## add column to display number of visitors in millions
  filter(parkname == 'Crater Lake' | parkname == 'Joshua Tree' | parkname == 'Zion') %>% ## filter for rows of interest only
  arrange(year) ## arrange year in ascending order

CJTZ_data$year <- as.numeric(CJTZ_data$year) ## convert "year" variable from character to numeric

CJTZ_data %>% ggplot(aes(x=year, y=visitors_mil, col=parkname)) + ## initiate ggplot with year on x-axis and number of visitors on y-axis colored by the park name
  geom_line(lwd=1.5) + ## create line graph and slightly increase line width
  scale_x_continuous(breaks=seq(1900, 2020, 10)) + ## scale the x-axis to only show every 10 years to make x-axis more visually appealing
  labs(title="Number of Visitors to Crater Lake, Joshua Tree, \nand Zion National Park from 1904 - 2016", x="Year", y="Number of Visitors (in millions)", col="National Park") ## add main title, axis labels and legend title
```

**Question 1b) Do the same but for the number of visitors normalized by state population for the state that contains the park.** 

``` {r}
state_pop$year <- as.numeric(state_pop$year) ## convert "year" variable from character to numeric in state_pop dataset

CJTZ_data_join <- inner_join(CJTZ_data, state_pop, by=c('state' = 'state', 'year' = 'year')) ## join park_visits and state_pop dataset to have each state park connected with the population

CJTZ_data_final <- CJTZ_data_join %>%
  mutate(visit_norm = visitors/pop) ## add a column for normalizing the number of visitors by state population

CJTZ_data_final %>% ggplot(aes(x=year, y=visit_norm, col=parkname)) + ## initiate ggplot with year on x-axis and normalized number of visitors on y-axis colored by the park name
  geom_line(lwd=1.5) + ## create line graph and slightly increase line width
  scale_x_continuous(breaks=seq(1900, 2020, 10)) + ## scale the x-axis to only show every 10 years to make x-axis more visually appealing
  labs(title="Number of Visitors to Crater Lake, Joshua Tree, and Zion National Park \nNormalized by State Population from 1904 - 2016", x="Year", y="Number of Visitors/State Population", col="National Park") ## add main title, axis labels and legend title
```

**Question 2: Run a simulation for all three parks (like our restaurant letter grade simulation in class) where you assume the probability of visiting each of the parks in both years (1941 and 1942) are the same. Plot a distribution for the number of people who visited in 1942 from your simulations and compare it to the number of people who actually visited the park in 1942.**

```{r}
set.seed(1771) ## set seed for reproducibility

park_sim <- function(park_name) { ## initiate function with park name as the variable
  year_park <- CJTZ_data_final %>% 
    filter((year==1941 | year==1942) & parkname==park_name) ## create a new data frame with the number of visitors for the selected park name in 1941 and 1942
  year_park_visitors <- year_park$visitors ## create a vector of the two numbers of visitors for the simulation
  sim_42 <- rbinom(1000, (year_park_visitors[2] + year_park_visitors[1]), p=0.5) ## simulate the visitors visiting the park; a success being that they visited the park in 1942
  hist(sim_42, ##plot the simulation as a histogram
       xlab='Simulated Number of Visitors', main=paste('Distribution of Simulated Visitors at', as_label(enquo(park_name)), 'in 1942'), ## add x-axis label and title
       xlim=c(year_park_visitors[2], max(sim_42))) ## set x-axis limit to visualize observed line and histogram of simulation
  abline(v=year_park_visitors[2], col='blue', lwd=3) ## add vertical line to represent the actual number of visitors to the park that year
  text(year_park_visitors[2], 50, 'Actual Visitors', pos = 4) ## add text to describe line
  }

map(c('Crater Lake', 'Joshua Tree', 'Zion'), park_sim)

```

**Question 3: Summarize your findings from Questions 1 and 2.**

Question 1 plots the number of visitors at 3 national parks (Zion, Joshua Tree, and Crater Lake) by year. The first graph shows the number of visitors at each park increases over time. By looking only at the first graph, one may believe the number of visitors truly did increase over the years. An important confounding variable in the first graph is the population in that state. The second graph again plots the number of visitors, but this time normalized by the state's population. Now the second graph shows the number of visitors at Crater Lake and Joshua Tree as somewhat flat lines, but the number of visitors at Zion is still increasing over time. Another potentially confounding variable in this graph is if the park visitors are actually residents of the state the park is in. Many Americans travel to National Parks as a destination. 

Question 2 depicts simulations of park visitors in 1942. Assuming the park visitors steadily increased over time, we should have been able to simulate a distribution around the actual number of visitors that year. For each of the graphs, it is clear the number of visitors that actually went to the park that year was significantly low. This could be explained by World War II occurring during that time causing people to not visit national parks as often. 
